Consistency scores in text data

### 2020-07-20 outputs/documents/paper.Rmd
Update abstract and introduction.

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    toc: false
    fig_caption: true
    latex_engine: pdflatex
    template: templates/svm-latex-ms.tex
bibliography: "references.bib"
header-includes:
  -  \usepackage{hyperref}
biblio-style: apalike
title: "Consistency scores in text data"
thanks: "A Shiny app for interactive and small-scale examples is available: HERE. An R package for larger scale applications is available: HERE. Our code and datasets are available: HERE. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
author:
- name: Rohan Alexander
  affiliation: University of Toronto
- name: Ke-Li Chiu
  affiliation: University of Toronto  
abstract: "In this paper we introduce a process to clean the text extracted from PDFs using GPT-3. Our approach compares originally extracted text with the text generated from GPT-3 using earlier text as stimulus. To guide this process, we introduce the notion of a consistency score, which refers to the proporation of text that is unchanged by the model. This is used to monitor changes during the cleaning process, and to compare the messiness of different texts. We illustrate our process on text from the Canadian Hansard and introduce both a Shiny application and an R package to make our process easier for others to adopt."
keywords: "text-as-data; GPT-3; quantitative analysis; cleaning."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
endnote: no
graphics: yes
---

@@

The model that we use to forecast is GPT-3 by OpenAI. OpenAI is an artificial intelligent research group who claims to be an pursuer of beneficial artificial general intelligence. Their works, including GPT-3, have a focus on generative models who have the capacity to generate data tha resemble human creation. GPT-3, the Generative Pretrained Transformer 3, is an unsupervised language model that has more than 175 billions of parameters, referring to the weights of the connections that enable the neural network to learn **(Keli add citation)**. GPT-3 can learn NLP tasks with few examples and without task-specific dataset **(Keli add citation)**. This means GPT-3 can learns like human do, which makes the creation of NLP technologies more accessible.

We apply our approach to the Canadian Hansard. The Canadian Hansard was digitised by **(Rohan add ref)**. This was a process by which PDFs were scanned, put through optical character recognition (OCR), and then corrected to a reasonable extent. The dataset is extensive, fit-for-purpose, and, appropriately, it has been used considerably **(Rohan add refs)**. However, there are many issues with the dataset in terms of reading it. We focus on one particular year - **(Rohan pick one)** - and show that our approach can be used to relatively quickly improve the quality of the dataset in a reproducible and consistent manner.

@@

OpenAI's GPT-3 is a generative, pre-trained, task-agnostic, language model that was released by OpenAI in **Ke-Li add month** 2020 **(Ke-Li add ref)**. OpenAI is **(Ke-Li add background)**. GPT-3 is the **Ke-Li add number X** model publicly released by OpenAI. It has '175 billion parameters' and OpenAI claim that it as the 'capacity to generate text that ressembles human creation' **(Ke-Li add ref)**. Initial research has found... **(Ke-Li please find papers that use it, describe them, and add refs - look on arXiv)**.

>>>>

---
output: 
  bookdown::pdf_document2:
    citation_package: natbib
    keep_tex: false
    toc: false
    fig_caption: true
    latex_engine: pdflatex
    template: templates/svm-latex-ms.tex
bibliography: "references.bib"
header-includes:
  -  \usepackage{hyperref}
biblio-style: apalike
title: "Consistency scores in text data"
thanks: "Thank you to X, Y and Z for helpful comments. A Shiny application for interactive and small-scale examples is available: https://kelichiu.shinyapps.io/Arianna/. An R package for larger scale applications is available: **HERE**. Our code and datasets are available: https://github.com/RohanAlexander/consistency_scores_in_text_datasets. Comments on the `r format(Sys.time(), '%d %B %Y')` version of this paper are welcome at: rohan.alexander@utoronto.ca."
author:
- name: Rohan Alexander
  affiliation: University of Toronto
- name: Ke-Li Chiu
  affiliation: University of Toronto  
abstract: "In this paper we introduce a process to clean the text extracted from PDFs using various methods from natural language processing. Our approach compares originally extracted text with the text generated from, or expected by, these methods using earlier text as stimulus. To guide this process, we introduce the notion of a consistency score, which refers to the proportion of text that is unchanged by the model. This is used to monitor changes during the cleaning process, and to compare the messiness of different texts. The methods that we consider are: n-grams, SOMETHING, GPT-2, and GPT-3. We illustrate our process on text from the Canadian Hansard and introduce both a Shiny application and an R package to make our process easier for others to adopt."
keywords: "text-as-data; natural language processing; GPT-3; quantitative analysis."
date: "`r format(Sys.time(), '%B %d, %Y')`"
geometry: margin=1in
fontfamily: mathpazo
fontsize: 12pt
# spacing: double
endnote: no
graphics: yes
---

@@

We consider various natural language processing methods. These include n-grams, **SOMETHING**, as well as GPT2 and GPT-3. The n-gram approach involves identifying two, three, or more, words that are commonly found together. Here think of a two-gram involving the word 'good' 'good morning'. At scale these can identify missing or unusual words, and work quickly, but they lack nuance. For instance an equally reasonable two-gram involving the word 'good' is 'good work'. For that reason we consider pre-trained generative models. These include **SOMETHING**, which works **SOMEHOW**. We also consider GPT-2 and GPT-3 from OpenAI. GPT-2 and GPT-3 are pre-trained generative unsupervised language models. They differ in the number of parameters. Generative Pretrained Transformer (GPT)-2 has *X* parameters and GPT-3 has more than 175 billions parameters. While GPT-2 is more limited, it can be run on smaller machines, whereas GPT-3 cannot.

We apply our approach to the Canadian Hansard. The Canadian Hansard was digitised by @beelen2017digitization. This was a process by which PDFs were scanned, put through optical character recognition (OCR), and then corrected to a reasonable extent. The dataset is extensive, fit-for-purpose, and, appropriately, it has been used considerably, for instance @rheault2020word. However, there are many issues with the dataset in terms of reading it. We focus on one particular year - **(Rohan pick one)** - and show that our approach can be used to relatively quickly improve the quality of the dataset in a reproducible and consistent manner.

@@

OpenAI's GPT-3 is a generative, pre-trained, task-agnostic, language model that was released by OpenAI in **Ke-Li add month** 2020 **(Ke-Li add ref)**. OpenAI is **(Ke-Li add background)**. GPT-3 is the **Ke-Li add number X** model publicly released by OpenAI. It has '175 billion parameters' and OpenAI claim that it as the 'capacity to generate text that ressembles human creation' **(Ke-Li add ref)**. Initial research has found... **(Ke-Li please find papers that use it, describe them, and add refs - look on arXiv)**. 
These parameters refer to the weights of the connections that enable the neural network to learn **(Keli add citation)**. GPT-3 can learn NLP tasks with few examples and without a task-specific dataset **(Keli add citation)**.
